% Appendix A

\chapter{Virtual Reality}
\label{AppendixA}
\lhead{Appendix A. \emph{What is Virtual Reality}}

%The material provided in this appendix is taken from \\
%\href{http://www.sunilpatel.co.uk/thesistemplate.php}%{\texttt{http://www.sunilpatel.co.uk/thesistemplate.php}}

\section{What is Virtual Reality}% \LaTeX{}}

Virtual Reality is the future and it's a 3D complete environment in which everything provides a real-time feeling. Virtual reality is a buzzword today and it is popular nowadays in the future students can take lessons and classes in a virtual environment and companies like Amazon is also working on e-commerce virtual reality-based application. People can just wear a VR headset and in their homes, they can go to virtual e-commerce stores, and explore mental health treatment. There are lots of applications of virtual reality like VR in fashion design, mental health treatment, education, sports, military, medical training, etc.

\subsection{What is Augmented Reality}
In augmented reality, we used a real environment instead of the virtual environment. Snapchat uses augmented reality when we open a Snapchat camera then Snapchat provides different filters in which we can different objects The filters in which Snapchat lens scans our face and applies different cartoon shapes or filters or face changers etc. all possible because of augmented reality.

\subsection{Difference between Virtual Reality and Augmented Reality}
No external AR headset is required for experiencing augmented reality while a VR headset is required for experiencing a virtual environment. In virtual reality, everything is virtual like objects in a virtual environment while Augmented reality augments the real-world scene. Snapchat uses augmented reality when we open a Snapchat camera then Snapchat provides different filters in which we can different objects The filters in which Snapchat lens scans our face and the apply different cartoon shapes or filters or face changers etc. all possible because of augmented reality.